%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development Intern} % Job title
    {Infracloud Technologies} % Organization
    {Pune, Maharastra, India} % Location
    {May. 2018 - July. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on Different Frameworks Kubernetes(An open source system or automating deployment, scaling, and management of containerized applications).}
        \item {Designed a plugin for the Serverless framework(The Serverless framework helps you build serverless apps with radically less overhead and cost on top of already established cloud services such as AWS, Google Cloud etc.) to add support for Fission framework using the Fission API.}
        \item {Added fully automated functionality to create local serverless apps on serverless framework instead of using online cloud services.}
        \item {Created a npm installable package for the same plugin.}
        \item {Link: https://github.com/infracloudio/serverless-fission}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front-End Developer (Lead)} % Job title
    {Tripogenic } % Organization
    {Pilani, Rajasthan, India} % Location
    {Dec. 2016 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a Website from scratch using HTML, CSS, Javascript(for frontend) and Python-Django(for backend)}
        \item {Implemented a fully automated booking and planning system and a secure payment gateway for the website along with a database for client planning and management for people interested in organic travelling and backpacking through India.}
        \item {Founder: Vilom Oja}
      \end{cvitems}
    }

\end{cventries}
