%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/Tango-with-Django} % Role
    {Toy-C0mpiler} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Created a compiler in C language as a part of our coursework.}
        \item {The front-end components included lexer, syntax and semantic analyzer and parser and the back-end components include ast, symbol table and a code generator.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/Tango-with-Django} % Role
    {Rango-Tango with Django} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A web application based on the book Tango with Django which acts as a sorting system that help me organize my work and hence making my workflow more efficient.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/hackernews-react} % Role
    {Reactornews} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A web application created using HackerNews API and Reactjs which provides you with latest HackerNews articles in a tabular format hence streamlining my news updates.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/Unity-Robbie} % Role
    {Unity-Robbie} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A 2D Platformer Game created using C-sharp on the Unity Game Engine learning important points in the field of game design.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/LISP} % Role
    {Lisp Compiler} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Created a lisp compiler in C language.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/Flappy-AI} % Role
    {Flappy-AI} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Created a JavaScript based in browser game of flappy bird and implemented a neuroevolutionary algorithm to teach an intelligent agent how to play the game.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/Socket-Terminal AND https://github.com/gucifer/chat-server} % Role
    {Socket Terminal and chat Server} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented a toy terminal and chat server using sockets in C to improve my knowledge of socket programming.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Github Link: https://github.com/gucifer/Twitter-Blockchain} % Role
    {Twitter Blockchain} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A tweet retrieval system based on Natural Language Processing and a blockchain based voting system for fake/bad tweet detection and reporting thus creating a client based reporting system while removing a central controlling figure.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
